Brain Tumor Detection using Machine Learning Models

### 2021-08-04 slides.tex
moved results table at the bottom
correct image and added roll number of authors

\author[Rajarshi, Bhargav, Soptorshi, Brahmajit] {
	Bhargav Basu \texorpdfstring{\\} \and
	Soptorshi Bhattacharjee \texorpdfstring{\\} \and
	Brahmajit Das \texorpdfstring{\\} \and
	Rajarshi Sardar
}

@@

		\begin{itemize}
			\item Binarization
			\item Filtering
			\item Edge Detection
			\item Segmentation
		\end{itemize}

		\begin{block}{Segmentation}
			Image segmentation is the process of partitioning a digital image into multiple
			segments (sets of pixels, also known as image objects). The goal of
			segmentation is to simplify and/or change the representation of an image into
			something that is more meaningful and easier to analyze.
		\end{block}

>>>>

\author[Rajarshi, Bhargav, Soptorshi, Brahmajit] {
	Bhargav Basu (183313-21-0045) \texorpdfstring{\\} \and
	Soptorshi Bhattacharjee (183313-21-0050) \texorpdfstring{\\} \and
	Brahmajit Das (183313-21-0044) \texorpdfstring{\\} \and
	Rajarshi Sardar (183313-21-0055)
}

@@

		\begin{itemize}
			\item \textbf{Binarization}: Converting RGB image to Grayscale
				image.
			\item \textbf{Filtering}: Convolving the image using low-pass filter
				kernel to remove noise.
			\item \textbf{Edge Detection}: Identifying points in digital image
				at which the brightness changes sharply.
			\item \textbf{Segmentation}: Process of partitioning the digital
				image into multiple segments, with the goal of changing the
				representation of the image into sometimes more meaningful to
				analyze.
		\end{itemize}
